manuscript_outline

### 2025-05-28 docs/manuscript/paper.Rmd
more changes even though I said I wasn't going to

p1 <- ascaphus_mod$pred_plot +
  labs(x = "Incubation Temperature (°C)", y = "Days to Hatch") +
  lims(y = c(0, 50))

@@

```{r, fig.height= 4.5 , fig.align = 'center', fig.cap="Custom hatch timing models developed for four North American frog species. Models are parameterized from Moore 1939 and phenology is predicted using a randomly generated temperature regime with mean 16 °C (Panel A). Panel B shows the effective values for different mean daily temperatures for each species, which are effectively species-specific linearized developmental reaction norms."}

@@

p2.1 + p2.2 + plot_annotation(tag_levels = 'A')
```

>>>>

fmt <- "~R^2 ==  %.4f"
lab1 <- sprintf(fmt, ascaphus_mod$r_squared)
p1 <- ascaphus_mod$pred_plot +
  labs(x = "Incubation Temperature (°C)", y = "Days to Hatch") +
  lims(y = c(0, 50)) +
  annotate("text", x = 10, y = c(35), label = c(lab1),  hjust = 0, parse = TRUE)

@@

```{r, fig.height= 8 , fig.width= 6, fig.align = 'center', fig.cap="Custom hatch timing models developed for four North American frog species. Models are parameterized from Moore 1939 and phenology is predicted using a randomly generated temperature regime with mean 16 °C (Panel A). Panel B shows the effective values for different mean daily temperatures for each species, which are effectively species-specific linearized developmental reaction norms."}

@@

p2.1 / p2.2 + plot_annotation(tag_levels = 'A')
```
